\documentclass[12pt,a4paper,twoside,openright]{report}
\usepackage{preamble} % imported packages/macros/styling

% for commenting
\usepackage{xcolor}
\newcommand\az[1]{\textcolor{blue}{{\bf [AZ:} #1{\bf]}}}

\usepackage[sorting=none]{biblatex}
\addbibresource{ref.bib}

\begin{document}
% ----------------------------------------------------------------------

% title page
\pagestyle{empty}

\rightline{\LARGE \textbf{Yulin(Kyra) Zhou}}

\vspace*{60mm}
\begin{center}
	\Huge
	\textbf{Backdoor attacks on \\ NLP prompting} \\[10mm]
	\huge
	Computer Science Tripos -- Part II \\[4mm]
	Queens' College \\[4mm]
	\today \\[95mm]
\end{center}

\thispagestyle{empty}

% ----------------------------------------------------------------------

\pagestyle{plain}

\pagenumbering{roman}
\setcounter{page}{1}

% declaration of originality
\section*{Declaration}

 {
  \setlength{\parskip}{\bigskipamount}

  I, Yulin(Kyra) Zhou of Queens' College, being a candidate for Part II of the Computer Science Tripos, hereby declare that this dissertation and the work described in it are my own work, unaided except as may be specified below, and that the dissertation does not contain material that has already been used to any substantial extent for a comparable purpose.

  I, Yulin(Kyra) Zhou of Queens' College, am content for my dissertation to be
  made available to the students and staff of the University.

  \emph{Signed:} Yulin(Kyra) Zhou

  \setlength{\parskip}{\smallskipamount}

  \emph{Date:} \today
 }

% Acknowledgements
\section*{Acknowledgements}

I am deeply appreciative of the invaluable guidance provided by my supervisors, Aaron Zhao, Ilia Shumailov, and Robert Mullins, throughout the project. I am also grateful to Wenyang Zhou, Yuang Chen, and Will Yu for their constructive comments on this dissertation. Finally, I would like to extend my sincere thanks to Ramsey Faragher, Alastair Beresford, and Andy Rice, my Director of Studies, for their generous support over the past three years.

% proforma
\chapter*{Proforma}
 {\large
  \begin{tabular}{ll}
	  Candidate number:   & \bf ???                                      \\
	  Project Title:      & \bf Backdoor attacks on NLP prompting        \\
	  Examination:        & \bf Computer Science Tripos -- Part II, 2023 \\
	  Word Count:         & \bf ??? \footnotemark[1]                     \\
	  Code Line Count:    & \bf ??? \footnotemark[2]                     \\
	  Project Originator: & \bf Aaron Zhao                  \\
	  Project Supervisor: & \bf Aaron Zhao                       \\
	  Project Co-supervisor: & \bf Ilia Shumailov, Robert Mullins \\
  \end{tabular}
 }
\footnotetext[1]{This word count was computed}
\footnotetext[2]{This code line count was computed}
\stepcounter{footnote}

\section*{Original Aims of the Project}
In natural language processing, Pre-trained Language Models (PLM) based on deep neural networks are commonly fine-tuned for end-user tasks. However, limited training data poses a challenge for achieving high performance using this \emph{pre-train then fine-tune} approach. Prompt-based learning is a new paradigm that directly probes knowledge from the PLM without extensive fine-tuning to overcome this limitation. Nevertheless, advances in prompt-based learning raise security concerns, such as backdoor attacks, in which attackers create hidden model behaviour that specific input patterns can trigger. This project aims to compare the performance of different prompt-based models and assess their vulnerability to backdoor attacks with different settings.

\section*{Work Completed}
The project successfully fulfilled the proposed criteria and extensions and further explored additional questions and ideas that were triggered by my results. I developed an extensible and robust framework to re-implement and compare three published prompting models and investigated whether automated prompting outperforms manual prompting. Then I designed several backdoor attacks with different settings to exploit the vulnerabilities of the models. Additionally, I extended my project by adding a visualisation toolkit for word embeddings and a novel invisible backdoor attack.

\section*{Special Difficulties}

None.

% table of contents
\tableofcontents

% list of figures
% \listoffigures

% ----------------------------------------------------------------------
\newpage
\pagenumbering{arabic}
% main chapters
\input{sections/1_introduction.tex}
\input{sections/2_preparation.tex}
\input{sections/3_implementation.tex}
\input{sections/4_evaluation.tex}
\input{sections/5_conclusions.tex}

% ----------------------------------------------------------------------

\newpage
\pagenumbering{roman}
\printbibliography
\newpage
\appendix
\addappheadtotoc
\input{sections/appendix}

% don't forget to append the original project proposal

\end{document}